Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-11 paper.tex
A brief conclusion

The \boutiques specification adopts a bottom-up
approach where new features are progressively added when applications
or platforms require them.

>>>>

\boutiques is available at \url{https://github.com/boutiques}. We
welcome feedback, issue reporting and pull requests. \boutiques adopts
a bottom-up approach where new features are progressively added based
on feedback from applications and platforms. Beyond the technicalities
discussed in this paper, the availability of a solid core of
applications and platforms in the framework is key to its success,
which we plan to continuously enhance in the future.
